ext_risk_copula

### 2019-02-21 ext_risk_copula.Rmd
modified

#Ricker model :
```{r sim_ricker, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

rlist<-seq(from=range(qr1)[iqmin],to=range(qr1)[iqmax], by = qs[iqmin]/4)

@@

```{r sim_hassell, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

```{r sim_msmith, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

```{r sim_pennycuick, echo=F,  results="hide", cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,r_bf_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

```{r sim_verhulst, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

```{r sim_abrewer, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

>>>>

#Ricker model :
```{r sim_ricker, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

fromr<-range(qr1)[iqmin]
tor<-range(qr1)[iqmax]

if(fromr>tor){
  byr<--qs[iqmin]/4
}else{
  byr<-qs[iqmin]/4
}

rlist<-sort(seq(from=fromr,to=tor, by = byr))

@@

```{r sim_hassell, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

```{r sim_msmith, echo=F, cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

```{r sim_pennycuick, echo=F, cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,r_bf_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

```{r sim_verhulst, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

```{r sim_abrewer, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")
